\textsf{Are large language models superhuman chemists?}

### 2024-10-17 src/tex/ms.tex
humanset pie chart

% \begin{figure}[!htb]
%     \centering
%     \includegraphics{figures/question_count_barplot.pdf}
%     \caption{\textbf{Number of questions for different topics.} The topics have been assigned using a combination of a rule-based system (mostly based on the source the question has been sampled from) and a classifier operating on word embeddings of the questions. 
%     The figure shows that not all aspects of chemistry are equally represented in our corpus. The \chembench corpus, by design, currently focuses on safety-related aspects, which is also evident in \Cref{fig:question_diversity}. This figure represents the combined count of multiple-choice questions (\gls{mcq}) and open-ended questions.}
%     \label{fig:topic_barplot}
%     \script{plot_statistics.py}
% \end{figure}

@@

>>>>

\begin{figure}[!htb]
    \centering
    \includegraphics{figures/cb_corpus_v1.pdf}
    \caption{\textbf{Distribution of topics and required skills.} TThis circular plot illustrates the distribution of questions across various chemistry topics, along with the primary skills required to address them. The topics were manually classified, showing a varied representation across different aspects of chemistry. Each topic is associated with a combination of three key skills: Calculation, Reasoning, and Knowledge, as indicated by the colored bars. \chembench samples diverse topics and diverse skills, setting a high bar for \glspl{llm} to demonstrate human-competitive performance across a wide range of chemistry tasks.}
    \label{fig:corpus}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[]{figures/cb_humanset_v1.pdf}
    \caption{\textbf{Composition of the human subset.} The circular plot shows the distribution of topics and required skills in the human subset of the \chembench corpus. The human subset is a representative subset of the full corpus, with a balanced distribution of topics and skills.}
\end{figure}
